\begin{thebibliography}{10}

\bibitem{ri11}
  	Riva, G., (2011). The Key to Unlocking the Virtual Body: Virtual Reality in the Treatment of Obesity and Eating Disorders. Journal of Diabetes Science and Technology. Volume 5, Issue 2.
  			
\bibitem{ri13}
	Ferrer-García, M., Gutiérrez-Maldonado, J., Riva, G. (2013). Virtual reality based treatments in eating disorders and obesity: A review. Journal of Contemporary Psychotherapy, 43, 207-221.
	
\bibitem{gu10}
 	Guardia, D., Lafarguea, G., Thomas, P., Dodin, V., Cottencin, O., \& Luyat, M. (2010). Anticipation of body-scaled action is modified in anorexia nervosa. Neuropsychologia, Volume 48, Issue 13, Pages 3961-3966
 		
 \bibitem{lu14}
 	Luyat, M. (2014). Les apports de la psychologie cognitive et de la neuropsychologie dans la compréhension de l'anorexie mentale. Journal de thérapie comportementale et cognitive, 24, 114-121.
 	
 \bibitem{Bo98}
 	Botvinick, M., \& Cohen, J. (1998). Rubber hands ‘feel’ touch that eyes see. Nature, 391, 756.
 	
  	
 \bibitem{bl10}
 	Lopez, C., \& Blanke, O. (2010). Quand l'esprit met le corps à distance. La Recherche, 439, 48-51.
 	
 \bibitem{eh07}
 	Ehrsson H. H. (2007). The experimental induction of out-of-body experiences. Science , 317-1048.
 
 \bibitem{le07}
 	Lenggenhager, B., Tadi, T. Metzinger, T., \& Blanke, O. (2007). Video ergo sum: manipulating bodily self-consciousness. Science, 317, 1096–1099
 	
 
 \bibitem{sl09}
  	Mel Slater, M., Daniel Perez-Marcos, D., H. Henrik Ehrsson, H. H., \& Maria V. Sanchez-Vives, M. V. (2009).Inducing illusory ownership of a virtual body. Frontiers in Neuroscience, 3(2), 214-220.
  	
 \bibitem{sl08}
  	Slater, M., Spanlang, B., Frisoli, A., \& Sanchez-Vives, M.V. (2008). Virtual hand illusion induced by visual- proprioceptive and motor correlations. PLoS ONE 5(4): e10381.
   	
 \bibitem{pr14}
  	Preston, C., \& Ehrsson, H. H. (2014). Illusory changes in body size modulate body satisfaction in a way that is related to non-clinical eating disorder psychopathology. PLoS ONE 9(1): e85773.
  	
 \bibitem{ca02}
 	Cash, T. F., Fleming, E. C., Alindogan, J., Steadman L., \& Whitehead, A. (2002) Beyond Body Image as a Trait: The Development and Validation of the Body Image States Scale. Eat Disord: J Treat Prevent 10: 103–113.
 
 \bibitem{mo12}	
 	Mori, M.; MacDorman, K.F.; Kageki, N., "The Uncanny Valley [From the Field]," Robotics \& Automation Magazine, IEEE , vol.19, no.2, pp.98,100, June 2012 doi: 10.1109/MRA.2012.2192811
 	
 \bibitem{mc12}	
 	McDonnell, R., Breidt, M., \& Bülthoff, H. H. (2012). Render me real?: investigating the effect of render style on the perception of animated virtual humans. ACM Transactions on Graphics (TOG), 31(4), 91.
 	
 %\bibitem{mi13}
 %	Miles, H.C.; Pop, S.R.; Watt, S.J.; Lawrence, G.P.; John, N.W.; Perrot, V.; Mallet, P.; Mestre, D.R., "Investigation of a Virtual Environment for Rugby Skills Training," Cyberworlds (CW), 2013 International Conference on , vol., no., pp.56,63, 21-23 Oct. 2013
 %	doi: 10.1109/CW.2013.45
 	
 %\bibitem{mi10}
 %	Michael Geuss, Jeanine Stefanucci, Sarah Creem-Regehr, and William B. Thompson. 2010. Can I pass?: using affordances to measure perceived size in virtual environments. In Proceedings of the 7th Symposium on Applied Perception in Graphics and Visualization (APGV '10). ACM, New York, NY, USA, 61-64. DOI=10.1145/1836248.1836259 http://doi.acm.org/10.1145/1836248.1836259 
 	
 \bibitem{sla09}
 	Slater, M., Khanna, P., Mortensen, J., Insu Yu, "Visual Realism Enhances Realistic Response in an Immersive Virtual Environment," Computer Graphics and Applications, IEEE , vol.29, no.3, pp.76,84, May-June 2009 doi: 10.1109/MCG.2009.55
 	
 \bibitem{zh09}
 	Zhong, Y. Q., Liu, H. Y., Jiang, J. F., \& Liu L. (2009). 3D Human Body Morphing Based on Shape Interpolation. The 1st International Conference on Information Science and Engineering, p1027-1030.
 	
 \bibitem{le01}
	 Lee, W., Magnenat-Thalmann N. (2001). Virtual Body Morphing Computer Animation, The Fourteenth Conference on Computer Animation. Proceedings, p158-166
 	
 \bibitem{kn07}	
 	Knossow, D. (2007).Paramétrage et Capture Multicaméras du Mouvement Humain. Human-Computer Interaction. Institut National Polytechnique de Grenoble - INPG.
 	
 \bibitem{zo12}
 	Zong, C. (2012). Systèeme embarquée de capture et analyse du mouvement humain durant la 	marche. Automatic. Université Pierre et Marie Curie - Paris VI.
  	
  \bibitem{ku12}
  	Kuntz, S., \& Cíger, J. (2012). Low-cost and home-made immersive systems. The International Journal of Virtual Reality, 11(3), 9-17.
  	
  \bibitem{ze12}	
  	Zhang, Z. (2012). Microsoft Kinect Sensor and Its Effect. MultiMedia, IEEE, vol. 19, no.2, pp. 4-10
 	
 \bibitem{ch12}	
 	Chang, C., Lange, B., Zhang, M., Koenig, S., Requejo, P., Somboon, N., Sawchuk, A. A., \& Rizzo A. A. (2012). Towards Pervasive Physical Rehabilitation Using Microsoft Kinect. In International Conference on Pervasive Computing Technologies for Healthcare (Pervasive-Health), p159-162.
 	
  \bibitem{li12}
 	 Livingston, M. A., Sebastian, J., Ai, Z., \& Decker, J. W. (2012). Performance Measurementsfor the Microsoft Kinect Skeleton. Proc. IEEE Virtual Reality Workshops, pp.119 -120.13
  
  \bibitem{oc12}
  	Oculus, V. R. (2012). Oculus Rift. Available from WWW: http://www. oculusvr. com/rift.
  
  \bibitem{lu15}
  	Lun, R., \& Zhao, W. (2015). A Survey of Applications and Human Motion Recognition with Microsoft Kinect. International Journal of Pattern Recognition and Artificial Intelligence.
  	
  \bibitem{ch15}
  	Chen G., Li J., Wang B., Zeng J., Lu G., and Zhang D. (2015) Reconstructing 3D human models with a Kinect, Comp. Anim. Virtual Worlds, doi: 10.1002/cav.1632.
  	
\end{thebibliography}

